### 2023-03-02 intro.qmd
update

The last part of the question is out of the scope of this manuscript but it should be said that a lot of uncertainties orbit around those carbon deficits, namely parameters used to estimate the metabolic activity of deep ocean organisms as well as deep food web dynamics and unquantified carbon sources such as the contribution of slowly settling particles and better estimation of POC fluxes \[@Burd2010-hc; @Martin2020-wa\].

@@

The size of aggregates was usually thought to be a key predictor of settling velocity \[e.g. @Passow2006-hw\] which is coherent with @eq-sinking-speed. However, @Iversen2020-kb did not find evidence for a size-sinking relationship therefore suggesting that excess density would be the main controlling factor. Because the sinking speed determines the time available for degradation in the water column, it also directly impacts the potential for carbon sequestration. With all things considered, there is a thus need for direct measurements of morphological characteristics (size, composition, porosity and density) of particles to better estimate their settling velocities \[@Iversen2020-kb; @Giering2020-zk; @Iversen2022-qj; @Williams2022-xx\].

@@

| Pump                   | POC export/injection depth range | DOC injection depth range | Sequestration time potential (years) |
|-----------------|------------------|-----------------|--------------------|
| Gravitational          | export depth - sediment          | None                      | N/A (142)                            |
| Mixed layer            | 200 - 1,000 m                    | 200 - 1,000 m             | 25 - 100 (54$^{b}$)                  |
| Eddy subduction        | 150 - 400 m                      | 150 - 400 m               | up to 150 (N/A)                      |
| Large-scale subduction | 200 - 1,000 m                    | 200 - 1,000 m             | 25 - 100 (54$^{b}$)                  |
| Diel migration         | 200 - 600 m                      | None                      | up to 250 (150$^{c}$)                |
| Seasonal migration     | 600 - 1,400 m$^{a}$              | None                      | up to 500 (N/A)                      |

>>>>

The last part of the question is out of the scope of this manuscript but it should be said that a lot of uncertainties orbit around those carbon deficits, namely parameters used to estimate the metabolic activity of deep ocean organisms as well as deep food web dynamics and unquantified carbon sources such as the contribution of slowly settling particles and better estimation of POC fluxes [@Burd2010-hc; @Martin2020-wa].

@@

The size of aggregates was usually thought to be a key predictor of settling velocity [e.g. @Passow2006-hw] which is coherent with @eq-sinking-speed. However, @Iversen2020-kb did not find evidence for a size-sinking relationship therefore suggesting that excess density would be the main controlling factor. Because the sinking speed determines the time available for degradation in the water column, it also directly impacts the potential for carbon sequestration. With all things considered, there is a thus need for direct measurements of morphological characteristics (size, composition, porosity and density) of particles to better estimate their settling velocities [@Iversen2020-kb; @Giering2020-zk; @Iversen2022-qj; @Williams2022-xx].

@@

| Pump                   | POC export/injection depth range | DOC injection depth range | Sequestration time potential (years) |
|-----------------|-------------------|-----------------|---------------------|
| Gravitational          | export depth - sediment          | None                      | N/A (142)                            |
| Mixed layer            | 200 - 1,000 m                    | 200 - 1,000 m             | 25 - 100 (54$^{b}$)                  |
| Eddy subduction        | 150 - 400 m                      | 150 - 400 m               | up to 150 (N/A)                      |
| Large-scale subduction | 200 - 1,000 m                    | 200 - 1,000 m             | 25 - 100 (54$^{b}$)                  |
| Diel migration         | 200 - 600 m                      | None                      | up to 250 (150$^{c}$)                |
| Seasonal migration     | 600 - 1,400 m$^{a}$              | None                      | up to 500 (N/A)                      |

### 2023-03-02 observingCarbonCycle.qmd
update

The use of transmissometers to characterize POC concentrations was shown by @Bishop1999-es who found that POC concentrations were well correlated with $c_{p}$, independently of ocean environment, season or depth. Subsequently, the idea of using a transmissometer as an OST was firstly applied by @Bishop2004-at where the magnitude of carbon export was quantified based on the particles accumulation on the upward-facing window of vertically oriented transmissometers on autonomous floats while they were drifting (i.e. parked at a specific depth). This method was later improved by [@Estapa2013-gw] who divided the attenuation signal into a continuous component, that is the regular accumulation of small particles on the transmissometer window and a discontinuous component resulting in positive jumps likely attributed to the deposition of (rarer) large particles (see @fig-estapa-method and @sec-case-study-labrador-sea). @Estapa2017-jr [-@Estapa2023-oz] further calibrated the OST carbon flux proxy using codeployed sediment traps and drifting transmissometers thus allowing the conversion of $c_{p}$ attenuation fluxes (units: m$^{-1}$d$^{-1}$) into carbon fluxes (units: mg C m$^{-2}$d$^{-1}$) using empirical POC-to-attenuance (ATN) ratio were ATN (unitless) is the product of $c_{p}$ and the transmissometer pathlength.

>>>>

The use of transmissometers to characterize POC concentrations was shown by @Bishop1999-es who found that POC concentrations were well correlated with $c_{p}$, independently of ocean environment, season or depth. Subsequently, the idea of using a transmissometer as an OST was firstly applied by @Bishop2004-at where the magnitude of carbon export was quantified based on the particles accumulation on the upward-facing window of vertically oriented transmissometers on autonomous floats while they were drifting (i.e. parked at a specific depth). This method was later improved by [@Estapa2013-gw] who divided the attenuation signal into a continuous component, that is the regular accumulation of small particles on the transmissometer window and a discontinuous component resulting in positive jumps likely attributed to the deposition of (rarer) large particles (see @fig-estapa-method and @sec-case-study-labrador-sea). [@Estapa2017-jr; -@Estapa2023-oz] further calibrated the OST carbon flux proxy using codeployed sediment traps and drifting transmissometers thus allowing the conversion of $c_{p}$ attenuation fluxes (units: m$^{-1}$d$^{-1}$) into carbon fluxes (units: mg C m$^{-2}$d$^{-1}$) using empirical POC-to-attenuance (ATN) ratio were ATN (unitless) is the product of $c_{p}$ and the transmissometer pathlength.
